Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
minor updates to Sec 2 and 3

\bo{I think this organization is great now!}

@@

\bo{Rewrote this, Mon Jun 1 a.m.}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
Here we will define $L$ to be consistent (Definition \bo{TODO}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \bo{TODO}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.

@@

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}
\botodo{On the right side, is measurable enough? I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$. Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}

>>>>

\bo{I think this organization is great!}

@@

\bo{Rewrote this, Mon Jun 1 a.m.}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
Here we will define $L$ to be consistent (Definition \ref{def:consistent-prop}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.

@@

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}
%% Bo: resolved, Jun 1
%\botodo{On the right side, is measurable enough? I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$. Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
%\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
